% cv-us.tex
% $Id: cv-us.tex,v 1.28 2006/12/12 22:53:52 jrblevin Exp $
%
% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2006 Jason R. Blevins
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents, however, I do ask that you
% please leave this notice and the above URL in the source code if you
% choose to redistribute this file.
%
% Jason R. Blevins <jrblevin@sdf.lonestar.org>
% http://jrblevin.freeshell.org
% Durham, December 12, 2006
%
%----------------------------------------------------------------------------%
% Copyright (C) 2007 Sylvain Bougerel
%
% Modification of the template. You are granted the same right as in the
% original document (see above). Likewise, the name of the orginial author
% and my name, and both copyrights should be left in the source code.
%
% Sylvain Bougerel
% Singapore, 12th July 2007
%
%%---------------------------------------------------------------------------%
%
% Notes:
%
% * Don't forget to change `pdfauthor' and `keywords' in the \hypersetup
%   section below.
%
% * To create a new page use: \newpage \opening
%
% * res.cls includes an \address{} command which can be used up to twice,
%   but my address is too long for the format it uses.
%
% * Alternate documentclass statement to put headings in margin:
%   \documentclass[margin,line,11pt,final]{res}
%
% * Can divide publication/presentation list into subsections by year:
%   \section{\bf\small\hspace{8mm}2006}
%
%%----------------------------------------------------------------------------%

\documentclass[overlapped,line,letterpaper]{res}

\usepackage{ifpdf}

\ifpdf
\usepackage[pdftex]{hyperref}
\else
\usepackage[hypertex]{hyperref}
\fi

\hypersetup{
  letterpaper,
  colorlinks,
  urlcolor=black,
  pdfpagemode=none,
  pdftitle={Curriculum Vitae},
  pdfauthor={Sylvain Bougerel},
  pdfcreator={$ $Id: cv-us.tex, v0.2 12/08/2016 18:35:18 Sylvain Bougerel $ $},
  pdfsubject={Curriculum Vitae},
  pdfkeywords={sylvain bougerel singapore linux unix C++ java C\# distributed
    computing high-availability large-scale command control quality team leadership
    gtk valgrind gcc gdb openvz}
}

%%===========================================================================%%

\begin{document}

%---------------------------------------------------------------------------
% Document Specific Customizations

% Make lists without bullets and with no indentation
\setlength{\leftmargini}{0em}
\renewcommand{\labelitemi}{}

% Use large bold font for printed name at top of pages
\renewcommand{\namefont}{\large\textbf}

%---------------------------------------------------------------------------

\name{Sylvain Bougerel}
\address{2 Marne Road\\
  \#02-06 Studios @ Marne\\
  Singapore 208393
}
\address{tel: +65 96673473\\
  sylvain.bougerel@gmail.com\\
  https://sg.linkedin.com/in/sylvain-bougerel-397b221
}

\begin{resume}

  %---------------------------------------------------------------------------

  \section{\bf General}
  French nationality. Born on 23rd September 1981.

  Fluent in French and English, basic conversational German.

  %---------------------------------------------------------------------------

  \section{\bf Background}

  In spite of my management-oriented career in Thales, I am still very much a
  technical person at heart. The reason why I am seeking new horizon today, is
  because I feel that I have reached the peek of my technical potential in
  Thales. I have always been looking for more challenges in my career, and while
  Thales has been offering me more responsibilities in the past few years,
  technically speaking, it fell short. I am now looking for a position in a
  company more driven by technical achievements with a clear vision.

  %---------------------------------------------------------------------------

  \section{\bf Education}

  \begin{format}
    \title{l}\dates{r}\\
    \body\\
  \end{format}

  \title{\em Master of Science in Software Engineering}
  \dates{2003--2005}
  \begin{position}
    University of Technology of Belfort-Montb\'{e}liard, France\newline
    Final year exchange program at the National University of Singapore
  \end{position}

  \title{\em Bachelor of Science in Software Development}
  \dates{2000--2002}
  \begin{position}
    University of Paris, South, Science Faculty of Orsay, France
  \end{position}

  %---------------------------------------------------------------------------

  \section{\bf Professional Experience}

  %At Thales Security Asia Pte Ltd, Singapore:

  \begin{format}
    \title{l}\dates{r}\\
    \employer{l}\location{r}\\
    \body\\
  \end{format}

  \title{\em Project Manager}
  \employer{Thales Solution Asia Pte Ltd
    (\href{http://www.thalesgroup.com}{www.thalesgroup.com})}
  \location{Singapore}
  \dates{2015--Present}
  \begin{position}
    Under my leadership, the project {\em NEL Upgrade} is increasing its gross
    margin year-on-year by 2\%, from 21.5\% to 23.5\%. More importantly, the
    customer has remained confident and satisfied of our team's deliveries,
    which has brought us an additional S\$400k in sales from 2015 to 2016,
    growing the overall sales to 21.9 millions.
  \end{position}

  \title{\em Software Manager}
  \employer{Thales Solution Asia Pte Ltd
    (\href{http://www.thalesgroup.com}{www.thalesgroup.com})}
  \location{Singapore}
  \dates{2011--2015}
  \begin{position}
    Heading the development team of the project {\em NEL upgrade} comprising of
    up to 10 Software Engineers. The software management position was the
    largest work package of the project. I built the entire software development
    tool chain and contributed updates and fixes to the project regularly. My
    leadership contributed directly to the timely delivery of the project.
  \end{position}

  \title{\em Deputy Technical Manager}
  \employer{Thales Security Asia Pte Ltd
    (\href{http://www.thalesgroup.com}{www.thalesgroup.com})}
  \location{Singapore}
  \dates{2009--2011}
  \begin{position}
    In charge of the design and integration of three core component interfaces
    for the project {\em Mexico Ciudad Segura}, involving thrid-party
    organisations. At the start of my assignment, I was responsible for the
    development of an AVL tracking component. Additionally, I contributed
    software design and bug fixes.
  \end{position}

  \newpage
  
  \title{\em Senior Software Developer \& Team Leader}
  \employer{Thales Information Systems Pte Ltd
    (\href{http://www.thalesgroup.com}{www.thalesgroup.com})}
  \location{Singapore}
  \dates{2007--2009}
  \begin{position}
    Involved with porting the {\em Singapore Police Coast Guard} surveillance
    system from HP--RT to Linux. Subsequently, I led the team of 5 developers to
    extend the code base of 2 million lines with new features. My
    personal assignment was to develop an new radar interface; the sales price
    of 400k for that work yielded a 180k margin as I completed the development 3
    months ahead of schedule. The project's margin financed my work on the
    next generation {\em New Coastal Surveillance System}.
  \end{position}

  %----------------------------------------------------------------------------


%%   \section{\bf Technical Skills}
%%   \em{}C/C++ development\em{}: GCC, GNU Autotools (autoconf, automake, libtool),
%%   STL, Boost, Lex/Yacc, Gdb, Gprof, Valgrind.

%%   \em{}Java Frameworks\em{}: ServiceMix, ActiveMQ JMS, parts of J2EE (Java WS*,
%%   JABX, XMLBeans).

%%   \em{}.Net Framework\em{}: Microsoft Visual Studio .Net, C\#, WCF, LinQ and
%%   Entity Framework, Ant Profiling tools.

%%   \em{}Web technologies\em{}: Python, Php, Perl, Javascript, SOAP, XML, XSD,
%%   RelaxNG, WSDL, AJAX.

%%   \em{}User interface and toolkit\em{}: Qt3.3, Gtk2 with Glade, OpenGL, SDL,
%%   X11/Motif, Swing.

%%   \em{}Database and Object Modeling\em{}: UML, SQL, PL/SQL, Oracle SQL (with
%%   experience in partitioning), PostgreSQL (with experience on Gist trees),
%%   BerkeleyDB, MySQL, SQLlite.

%%   \em{}Applications\em{}: Linux (Debian, ArchLinux, Redhat, Ubuntu, over 10 year
%%   of personal use), CVS, SVN, Git, Emacs, Vi(m), Doxygen, Nmap, Tcpdump, Strace,
%%   CodeSynthesis XSD, Sysprof, Vmware, Visual Studio 9, TFS, SQL Sever
%%   2008, MS Project, MS Visio (design and code generation).

%%   \em{}Quality and estimation techniques\em{}: continuous integration and unit
%%   testing using TFS, WBS-based estimation, Function Point Analysis,

  %\section{\bf Presentations}
  %
  %``Solving Nonlinear Wave Equations with Mathematica,''
  %North Carolina State University, April 23, 2003.

  %----------------------------------------------------------------------------

  \section{\bf Professional Training and Certifications}

  \begin{format}
    \title{l}\dates{r}\\
    %\location{l}\\
    \body\\
  \end{format}

  \title{\em Coached in Scrum Methodologies}
  \dates{March 2012--Present}
  %\location{Singapore}
  \begin{position}
    With more than 300 hours of ongoing coaching in Scrum methodologies with a
    certified Agile Consultant, I have acquired solid hand-on experience to lead
    an Agile development team.
  \end{position}

%%   \title{\em{Passport for System Engineering} }
%%   \dates{September 2010}
%%   %\location{Singapore}
%%   \begin{position}
%%     4 days training on System Engineering methodologies applied to the work
%%     place and provided by Thales Solution Asia Pte Ltd.
%%   \end{position}

  %% \title{\em{Software Development Effort Estimation} }
  %% \dates{April 2010}
  %% %\location{Singapore}
  %% \begin{position}
  %%   3 days training on Function Point Analysis, one of the few ISO recognized
  %%   software metric.
  %% \end{position}

  %%\newpage

  \title{\em RD236 Red Hat Linux Kernel Internals}
  \dates{April 2006}
  %\location{Singapore}
  \begin{position}
    Hands-on course designed to provide a detailed examination of the
    Linux kernel architecture and its modules.
  \end{position}

  %%===========================================================================%%
  %% \opening

  %------------------------------------------------------------------------------

  \section{\bf Details of Recent Projects}

  \begin{format}
    \title{l}\dates{r}\\
    \body\\
  \end{format}

  \title{\em North East Line ISCS Upgrade (NEL Upgrade)}
  \dates{July\ 2011--Present}
  \begin{position}
    The North-East Line ISCS enables only 6 operators to run the entire fleet of
    32 driver-less trains, monitor the 40km of tracks, the various energy
    circuits (air, water, electricity) and efficiently communicate among
    operators, contractors and the public. With it's very large number of
    interfaces and its direct impact on the population, this upgrade is a
    critical undertaking.
    \newline
    {\bf Technologies:} JIRA, Git, Jenkins, VMWare, Sikuli, Linux, C++, Tcl/Tk, Python, Gdb.
  \end{position}

  \title{\em Mexico Ciudad Segura}
  \dates{October\ 2009--June\ 2011}
  \begin{position}
    In 2009, Thales Group has been awarded with the deployment of a new
    integrated call center and security system for Mexico City.  This was
    Thales' largest integrated call center ever to be rolled out. Some key
    figures: 6 operation centers to deploy, 8000 cameras to control, 25000
    ground resources to manage, 40000 calls received per day, 8 Millions people
    to protect.
    \newline
    {\bf Technologies:} JIRA, SVN, C\# (with .Net components WCF, WPF, LinQ), TFS, MSSQL, ActiveMQ,
    ServiceMix.
  \end{position}

  \title{\em New Coastal Surveillance System}
  \dates{May\ 2008--September\ 2009}
  \begin{position}
    The new system is designed to provide a greater level of high-availability,
    scalability and ease of development. In 2013, this product became the basis
    of our offer in costal surveillance systems and has been sold to 3
    governmental organisations since.
    \newline
    {\bf Technologies:} SVN, ActiveMQ JMS, XSD, C++, Boost (Asio), Java, Python, Linux,
    Gdb, Valgrind.
  \end{position}

  \title{\em Singapore Police Coast Guard}
  \dates{May\ 2006--April\ 2008}
  \begin{position}
    The supervision system monitoring the maritime traffic of
    Singapore waters. The system fuses the data from 5 main radars and
    several mobile radars in order to render a syntetic view of the 2000
    marine vessels circulating in the busy waters of Singapore.
    \newline
    {\bf Technologies:} Linux, C++, Lex/Yacc, OpenVZ, Valgrind, Gdb, X11/Motif.
  \end{position}

  %% \title{\em Singapore Civil Defense Force archiving system}
  %% %\title{SCDF Archiving System}
  %% %\title{\em Software Developer}
  %% \dates{September\ 2005--April\ 2006}
  %% \begin{position}
  %%   Design and developed over 8 months a C\#/ASP.Net--based archiving system for
  %%   the Singapore Civil De-fence Force with work-flow management of the
  %%   document.
  %% \end{position}

  %---------------------------------------------------------------------------

  \section{\bf Personal Interests}

  Passionate about Linux and open-source, working since 2009 on the
  open-source Spatial C++ Library, the spiritual child of the library
  libkdtree++, which I maintained for a short period of time.

  An avid badminton player, who enjoys living, traveling and diving around
  South-East Asia.

  %---------------------------------------------------------------------------

  %% \begin{center}
  %%   \vspace{\fill}\ \newline
  %%          {\tiny \rm $ $Author: Sylvain Bougerel $ $ }
  %%          {\tiny \rm $ $Date: 4/8/2016 $ $ }
  %%          %{\tiny \rm $ $Revision: 0.2 $ $ }
  %% \end{center}

\end{resume}

\end{document}

%%===========================================================================%%
